\bf Looking at Non-Linear Dimension Reductions as Models in the Data Space

### 2024-06-11 paper.qmd
subscripts used in notation diagram, and caption fixed

```{r}
#| label: tbl-notation
#| tbl-cap: "Summary of notation for describing new methodology."
# Notations used in the paper

@@

```{r}
hex_param_vis <- ggplot(data = hex_grid, aes(x = x, y = y)) + 
    geom_polygon(fill = "white", color = "#bdbdbd", aes(group = hex_poly_id)) +
    geom_point(data = all_centroids_df, aes(x = c_x, y = c_y), color = "#31a354", size = 0.9) +
    geom_point(data = all_centroids_df |> dplyr::filter(hexID == 1), aes(x = c_x, y = c_y), color = "black") + ## starting point
    geom_rect(aes(xmin = 0 - 0.03, xmax = 1 - 0.03, ymin = 0 - 0.05, ymax = r2- 0.05), fill = "white", color = "black", alpha = 0, linewidth = 0.7) +
    geom_segment(x = 0 - 0.03, y = -0.35, xend = 1 - 0.03, yend = -0.35,
                 arrow = arrow(length = unit(0.03, "npc"), ends = "both"), color = "black")+
    annotate("text", x=0.5, y=-0.45, label= "r1", color = "black") +
    geom_segment(x = -0.25, y = 0 - 0.05, xend = -0.25, yend = r2 - 0.05,
                 arrow = arrow(length = unit(0.03, "npc"), ends = "both"), color = "black")+ 
    annotate("text", x=-0.35, y=1, label= "r2", color = "black") +
    geom_segment(x = -0.1 + 0.2087578, y = -0.15, xend = -0.1 + 0.2087578*2, yend = -0.15,
                   arrow = arrow(length = unit(0.03, "npc"), ends = "both"), color = "black")+ # a1 = 0.2087578
    annotate("text", x=0.2, y=-0.25, label= "a1", color = "black") +
    geom_segment(x = -0.15, y = -0.1*r2 + 0.1807896*2, xend = -0.15, yend = -0.1*r2 + 0.1807896*3,
                     arrow = arrow(length = unit(0.03, "npc"), ends = "both"), color = "black")+ # a2 = 0.1807896
    annotate("text", x=-0.15, y=0.45, label= "a2", color = "black") +
    annotate("text", x=-0.18, y=-0.45, label= "(s1, s2)", color = "black") ## starting point
```

```{r}
#| label: fig-hex-param
#| fig-cap: "Notations for hexagonal grid configurations."
#| out-height: 30%
#| fig-width: 2
#| fig-height: 3
#| fig-pos: H

@@

```{r}
#| echo: false
#| label: fig-lg-scurve
#| fig-pos: H
#| fig-cap: "$2\\text{-}D$ model generated for different benchamrk values to remove long edges: (a) benchmark = $0.201$ (default), (b) benchmark = $0.35$, and (c) benchmark = $1.1$. What is the effective benchmark value to remove long edges?"
#| fig-width: 6
#| fig-height: 3

>>>>

```{r}
#| label: tbl-notation
#| tbl-cap: "Summary of notation for describing new methodology."
# Notation used in the paper

@@

```{r}
# Code to draw illustration for notation
hex_param_vis <- ggplot(data = hex_grid, aes(x = x, y = y)) + 
    geom_polygon(fill = "white", color = "#bdbdbd", aes(group = hex_poly_id)) +
    geom_point(data = all_centroids_df, aes(x = c_x, y = c_y), color = "#31a354", size = 0.9) +
    geom_point(data = all_centroids_df |> dplyr::filter(hexID == 1), aes(x = c_x, y = c_y), color = "black") + ## starting point
    geom_rect(aes(xmin = 0 - 0.03, xmax = 1 - 0.03, ymin = 0 - 0.05, ymax = r2- 0.05), fill = "white", color = "black", alpha = 0, linewidth = 0.7) +
    geom_segment(x = 0 - 0.03, y = -0.35, xend = 1 - 0.03, yend = -0.35,
                 arrow = arrow(length = unit(0.03, "npc"), ends = "both"), color = "black")+
    annotate("text", x=0.5, y=-0.45, label= expression(r[1]), color = "black") +
    geom_segment(x = -0.25, y = 0 - 0.05, xend = -0.25, yend = r2 - 0.05,
                 arrow = arrow(length = unit(0.03, "npc"), ends = "both"), color = "black")+ 
    annotate("text", x=-0.35, y=1, label= expression(r[2]), color = "black") +
    geom_segment(x = -0.1 + 0.2087578, y = -0.15, xend = -0.1 + 0.2087578*2, yend = -0.15,
                   arrow = arrow(length = unit(0.03, "npc"), ends = "both"), color = "black")+ # a1 = 0.2087578
    annotate("text", x=0.2, y=-0.25, label= expression(a[1]), color = "black") +
    geom_segment(x = -0.15, y = -0.1*r2 + 0.1807896*2, xend = -0.15, yend = -0.1*r2 + 0.1807896*3,
                     arrow = arrow(length = unit(0.03, "npc"), ends = "both"), color = "black")+ # a2 = 0.1807896
    annotate("text", x=-0.15, y=0.45, label= expression(a[2]), color = "black") +
    annotate("text", x=-0.18, y=-0.25, label= expression(group("(", list(s[1], s[2]), ")")), color = "black") ## starting point
```

```{r}
#| label: fig-hex-param
#| fig-cap: "Illustration of the components of the hexagon grid showing the notation used in explanations."
#| out-height: 30%
#| fig-width: 3
#| fig-height: 4.5
#| fig-pos: H

@@

```{r}
#| echo: false
#| label: fig-lg-scurve
#| fig-pos: H
#| fig-cap: "$2\\text{-}D$ model generated for different benchmark values to remove long edges: (a) benchmark = $0.201$ (default), (b) benchmark = $0.35$, and (c) benchmark = $1.1$. What is the effective benchmark value to remove long edges?"
#| fig-width: 6
#| fig-height: 3

### 2024-06-11 paper.tex
subscripts used in notation diagram, and caption fixed

\caption{\label{fig-hex-param}Notations for hexagonal grid
configurations.}

@@

\caption{\label{fig-lg-scurve}\(2\text{-}D\) model generated for
different benchamrk values to remove long edges: (a) benchmark =
\(0.201\) (default), (b) benchmark = \(0.35\), and (c) benchmark =
\(1.1\). What is the effective benchmark value to remove long edges?}

>>>>

\caption{\label{fig-hex-param}Illustration of the components of the
hexagon grid showing the notation used in explanations.}

@@

\caption{\label{fig-lg-scurve}\(2\text{-}D\) model generated for
different benchmark values to remove long edges: (a) benchmark =
\(0.201\) (default), (b) benchmark = \(0.35\), and (c) benchmark =
\(1.1\). What is the effective benchmark value to remove long edges?}
